---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r ragg, echo = FALSE}
knitr::opts_chunk$set(
  dev = "ragg_png"
)
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(tibble)
library(hrbragg)
library(ggplot2)

# current version
packageVersion("hrbragg")

```

For the moment, you'll need to install Inter:

```{r install-font, eval = FALSE}
install_inter()
```

### Inspect the definitions of the feature codes:

```{r ex-00}
str(inter_pkg, 1)

data("feature_dict")

feature_dict[feature_dict$tag %in% textshaping::get_font_features("Inter")[[1]],]
```

### Let's make a plot!

```{r ex-01}
ggplot() +
  geom_point(
    data = mtcars,
    aes(mpg, wt, color = factor(cyl))
  ) +
  geom_label(
    aes(
      x = 15, y = 5.48,
      label = "<- A fairly useless annotation\n       that uses the custom Inter\n          variant by default."
    ),
    label.size = 0, hjust = 0, vjust = 1
  ) +
  labs(
    x = "Fuel efficiency (mpg)", y = "Weight (tons)",
    title = "Seminal ggplot2 scatterplot example",
    subtitle = "A plot that is only useful for demonstration purposes",
    caption = "Brought to you by the letter 'g'"
  ) -> gg1
```

### Dark & light mode support with just a parameter change!

```{r dark-mode-01}
gg1 + theme_inter(grid = "XY", mode = "dark") 
```

Note the ligatures aren't as nice in Goldman Sans

```{r dark-mode-01-rc}
gg1 + theme_rc(grid = "XY", mode = "dark") 
```

### Note the ligatures aren't as nice in or Roboto Condensed

```{r dark-mode-01-gs}
gg1 + theme_gs(grid = "XY", mode = "dark") 
```

```{r light-mode-01}
gg1 + theme_inter(grid = "XY", mode = "light") 
```

```{r light-mode-01-rc}
gg1 + theme_rc(grid = "XY", mode = "light") 
```

```{r light-mode-01-gs}
gg1 + theme_gs(grid = "XY", mode = "light") 
```

### Making sure we got all the various plot components styled

```{r ex-02}
ggplot() +
  geom_point(
    data = mpg,
    aes(displ, hwy, color = trans)
  ) +
  facet_wrap(
    vars(cyl, drv), scales = "free", drop = TRUE
  ) +
  labs(
    x = "Displacement", y = "Highway",
    title = "Another seminal ggplot2 scatterplot example",
    subtitle = "A plot that is only useful for demonstration purposes",
    caption = "Brought to you by the letter 'g'"
  ) -> gg2
```

```{r light-mode-02, fig.width=1400/96, fig.height=700/96}
gg2 + theme_inter(grid = "XY", mode = "light") 
```

```{r dark-mode-02, fig.width=1400/96, fig.height=700/96}
gg2 + theme_inter(grid = "XY", mode = "dark") 
```

### Here's a way to preview any variants you create:

```{r preview-00, fig.width=600/96, fig.height=1300/96}
preview_variant(inter_pkg)
```

```{r preview-01, fig.width=400/96, fig.height=300/96}
reconfigure_font(
  family = "Trattatello",
  width = "normal",
  ligatures = "discretionary",
  calt = 1, tnum = 1, case = 1,
  dlig = 1, kern = 1,
  zero = 0, salt = 0
) -> trat

preview_variant(trat)
```

```{r preview-02, fig.width=600/96, fig.height=1100/96}
reconfigure_font(
  family = "Barlow",
  width = "normal",
  ligatures = "standard",
  tnum = 1, kern = 1
) -> barlow

preview_variant(barlow)
```

## hrbragg Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.
